### 2015-12-29 fundamentals/examples.tex
table cleanup

\begin{table}[H]
\centering
\begin{tabularx}{\columnwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Cycic &  Input control - embedded in Cyclist & \cite{flanagan_input_2013}\\
Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\
Ciclus & Continuous integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
Cycstub & Skeleton for clean slate module development & \cite{carlsen_cycstub_2014}\\
Cyan & \Cyclus analysis tool & \cite{carlsen_cyan_2014}\\
Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{carlsen_cloudlus_2014} \\
\hline
\end{tabularx}
\caption{Many tools have been developed outside of the scope of the \Cyclus kernel for improved user, developer, and analyst experiences with \Cyclus.}
\label{tab:coretools}
\end{table}

>>>>

\begin{table}[H]
\centering
\begin{tabularx}{\columnwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Cycic &  Input control embedded in Cyclist & \cite{flanagan_input_2013}\\
Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\
Ciclus & Continuous integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
Cycstub & Skeleton for clean slate module development & \cite{carlsen_cycstub_2014}\\
Cyan & \Cyclus analysis tool & \cite{carlsen_cyan_2014}\\
Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{carlsen_cloudlus_2014} \\
\hline
\end{tabularx}
\caption{Many tools have been developed outside of the scope of the \Cyclus kernel for improved user, developer, and analyst experiences with \Cyclus.}
\label{tab:coretools}
\end{table}
